Global patterns of forest autotrophic carbon fluxes

### 2020-08-07 manuscript/manuscript draft.Rmd
removed references from Table 1
#62

\renewcommand{\arraystretch}{2}
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
hypothesis_table <- read.csv("hypothesis_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
hypothesis_table[1,1] <- paste0(hypothesis_table[1,1], footnote_marker_number(1),"$^{,}$",footnote_marker_number(2),"$^{,}$", footnote_marker_number(3),"$^{,}$", footnote_marker_number(10))
hypothesis_table[2,1] <- paste0(hypothesis_table[2,1], footnote_marker_number(1),"$^{,}$",footnote_marker_number(4),"$^{,}$",footnote_marker_number(9))
hypothesis_table[3,1] <- paste0(hypothesis_table[3,1], footnote_marker_number(1),"$^{,}$",footnote_marker_number(4))
hypothesis_table[4,1] <- paste0(hypothesis_table[4,1], footnote_marker_number(5))
hypothesis_table[10,1] <- paste0(hypothesis_table[10,1], footnote_marker_number(6),"$^{,}$",footnote_marker_number(7),"$^{,}$", footnote_marker_number(8))
hypothesis_table[11,1] <- paste0(hypothesis_table[11,1], footnote_marker_number(7),"$^{,}$", footnote_marker_number(8))
hypothesis_table[12,1] <- paste0(hypothesis_table[12,1], footnote_marker_number(8))
kable(hypothesis_table, format = "latex", booktabs = TRUE, caption = "Summary of research questions, corresponding hypotheses, and results. Statistically signficant support for/ rejection of hypotheses is indicated with 'yes'/'no', and '-' indicates no significant relationship. Parentheses indicate partial overall support or rejection of hypotheses across all fluxes considered.", escape = F) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12) %>%
  pack_rows("Q1. How do C fluxes vary with latitude?", 1, 1, latex_gap_space = "1em", colnum = 5, hline_before = FALSE) %>%
  pack_rows("Q2. How do C fluxes vary with mean annual temperature (MAT) and precipitation (MAP)?", 2, 4, latex_gap_space = "1em", colnum = 5, hline_before = TRUE) %>%
  pack_rows("Q3. How are C fluxes related to other annual climate variables?", 5, 7, latex_gap_space = "1em", colnum = 5, hline_before = TRUE) %>%
  pack_rows("Q4. How does seasonality influence annual C fluxes?", 8, 11, latex_gap_space = "1em", colnum = 5, hline_before = TRUE) %>%
  pack_rows("Q5. When standardised by growing season length, how do annual C fluxes vary with climate?", 12, 15, latex_gap_space = "1em", colnum = 5, hline_before = TRUE) %>%
  add_header_above(c(" ",  " ", "Forest autotrophic carbon fluxes" = 9, " ")) %>%
  #column_spec(2:11, width = "1.8cm") %>%
  kableExtra::landscape() %>%
  kableExtra::footnote(number = c("Luyssaert et al. (2007)", "Gillman et al. (2015)", "Simova and Storch (2017)", "Schuur (2003)", "Taylor et al. (2016)", "Malhi (2012)", "Michaletz et al. (2014)", "Chu et al. (2016)", "Piao et al. (2010)", "Huston & Wolverton (2009)"), footnote_as_chunk = TRUE)
```

>>>>

\renewcommand{\arraystretch}{2}
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
hypothesis_table <- read.csv("hypothesis_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
#hypothesis_table[1,1] <- paste0(hypothesis_table[1,1], footnote_marker_number(1),"$^{,}$",footnote_marker_number(2),"$^{,}$", footnote_marker_number(3),"$^{,}$", footnote_marker_number(10))
#hypothesis_table[2,1] <- paste0(hypothesis_table[2,1], footnote_marker_number(1),"$^{,}$",footnote_marker_number(4),"$^{,}$",footnote_marker_number(9))
#hypothesis_table[3,1] <- paste0(hypothesis_table[3,1], footnote_marker_number(1),"$^{,}$",footnote_marker_number(4))
#hypothesis_table[4,1] <- paste0(hypothesis_table[4,1], footnote_marker_number(5))
#hypothesis_table[10,1] <- paste0(hypothesis_table[10,1], footnote_marker_number(6),"$^{,}$",footnote_marker_number(7),"$^{,}$", footnote_marker_number(8))
#hypothesis_table[11,1] <- paste0(hypothesis_table[11,1], footnote_marker_number(7),"$^{,}$", footnote_marker_number(8))
#hypothesis_table[12,1] <- paste0(hypothesis_table[12,1], footnote_marker_number(8))
kable(hypothesis_table, format = "latex", booktabs = TRUE, caption = "Summary of research questions, corresponding hypotheses, and results. Statistically signficant support for/ rejection of hypotheses is indicated with 'yes'/'no', and '-' indicates no significant relationship. Parentheses indicate partial overall support or rejection of hypotheses across all fluxes considered.", escape = F) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12) %>%
  pack_rows("Q1. How do C fluxes vary with latitude?", 1, 1, latex_gap_space = "1em", colnum = 5, hline_before = FALSE) %>%
  pack_rows("Q2. How do C fluxes vary with mean annual temperature (MAT) and precipitation (MAP)?", 2, 4, latex_gap_space = "1em", colnum = 5, hline_before = TRUE) %>%
  pack_rows("Q3. How are C fluxes related to other annual climate variables?", 5, 7, latex_gap_space = "1em", colnum = 5, hline_before = TRUE) %>%
  pack_rows("Q4. How does seasonality influence annual C fluxes?", 8, 11, latex_gap_space = "1em", colnum = 5, hline_before = TRUE) %>%
  pack_rows("Q5. When standardised by growing season length, how do annual C fluxes vary with climate?", 12, 15, latex_gap_space = "1em", colnum = 5, hline_before = TRUE) %>%
  add_header_above(c(" ",  " ", "Forest autotrophic carbon fluxes" = 9, " ")) %>%
  #column_spec(2:11, width = "1.8cm") %>%
  kableExtra::landscape() 
 # kableExtra::footnote(number = c("Luyssaert et al. (2007)", "Gillman et al. (2015)", "Simova and Storch (2017)", "Schuur (2003)", "Taylor et al. (2016)", "Malhi (2012)", "Michaletz et al. (2014)", "Chu et al. (2016)", "Piao et al. (2010)", "Huston & Wolverton (2009)"), footnote_as_chunk = TRUE)
```
